How many researchers use 'boilerplate' statistical analysis sections?

### 2021-03-09 manuscript/draft_manuscript.Rmd
Update draft_manuscript.Rmd

>>>>

Top matches (Topic 3)

* 10.1371/journal.pone.0043519: All statistical analyses were performed using GraphPad Prism (GraphPad Software Inc., San Diego, CA).
* 10.1371/journal.pone.0045453: GraphPad Prism (Graphpad Software, San Diego, CA) was used for all analyses.
* 10.1371/journal.pone.0170640: All statistical analysis of the data was performed using GraphPad Prism software (GraphPad Prism Software Inc., La Jolla, Ca).
* 10.1371/journal.pone.0036750: All statistical analysis was performed using Graphpad Prism software.
* 10.1371/journal.pone.0058148: All statistical analysis was performed using the Graphpad Prism software.
